\pkg{sdmTMB}: An \proglang{R} Package for Fast, Flexible, and User-Friendly Generalized Linear Mixed Effects Models with Spatial and Spatiotemporal Random Fields

### 2023-09-20 doc/paper-jss/sdmTMB-paper.Rnw
Add a few ideas on discussion - combine future ideas paragraphs into 1

@@

Additional functionality in \pkg{sdmTMB} not already mentioned includes
interpolating across missing time slices and forecasting, the barrier SPDE model
\citep{bakka2019}, time-varying spatiotemporal covariance parameters
\citep{ward2022}, and simulation from the parameter joint precision matrix.
Future development may include additional zero-inflated models, improvements to
Bayesian sampling efficiency \citep[e.g.,][]{monnahan2021}, continuous-time
models \citep[e.g.,][]{blangiardo2015book}, multivariate responses, and
non-Gaussian random fields \citep[e.g.,][]{anderson2019}. The included \pkg{TMB}
\texttt{.cpp} file provides a tested model template that can be modified to add
additional features.

There are several planned additions to the \pkg{sdmTMB} model structure.
A subset of features to be added in the near future includes (1) multivariate
models to allow for simultaneous modelling of data from multiple species, (2)
integration with the \pkg{RTMB} \citep{rtmb} package so that the model code base
will be written in \proglang{R} rather than \proglang{C++}, (3) inclusion of
a dispersion formula similar to \pkg{glmmTMB}, and (4) estimation of random
slopes.
% TODO random slopes looks gnarly to do generically?

>>>>

TODO add paragraph here on applications to other fields, beyond ecology and fisheries? Specifically thinkgin about:
- spatial econometrics (e.g. Elhorst, 2012; Lee & Yu, 2010)
- disease and medicine (e.g. Wakefield work)
- agriculture (https://link.springer.com/article/10.1007/s00122-019-03424-y)

@@

Additional functionality in \pkg{sdmTMB} not already mentioned includes
interpolating across missing time slices and forecasting, the barrier SPDE model
\citep{bakka2019}, time-varying spatiotemporal covariance parameters
\citep{ward2022}, and simulation from the parameter joint precision matrix.

There are several planned future additions to the \pkg{sdmTMB} model structure.
A subset of features to be added in the near future includes (1) multivariate
models to allow for simultaneous modelling of data from multiple species, (2)
integration with the \pkg{RTMB} \citep{rtmb} package so that the model code base
will be written in \proglang{R} rather than \proglang{C++}, (3) inclusion of
a dispersion formula similar to \pkg{glmmTMB}, (4) continuous-time
models \citep[e.g.,][]{blangiardo2015book}, (5) non-Gaussian random fields \citep[e.g.,][]{anderson2019}, and (6) multivariate responses. The included \pkg{TMB}
\texttt{.cpp} file is flexible and provides a tested model template that can be modified to add
additional features.
% TODO random slopes looks gnarly to do generically? EW: -- agree, I mostly have looked at glmmTMB / brms implementations
% removed random slopes -- another feature that could be added is 3D models, e.g. https://doi.org/10.1016/j.spasta.2023.100750
